### 2016-01-14 papers/CAFe/HIPS-paper/intro.tex
Added better citations to the OCR section.

Another option is to abandon the stricture of message passing within a procedural
programming language altogether.  The Open Community Runtime (OCR) project provides an
asynchronous task-based runtime designed for machines with high-core count, such as can be
expected in any exascale hardware design\cite{OCR:SC:2012}.  The project's goal is to
create a framework and reference implementation to help developers explore programming
methods to improve the power efficiency, programmability, and reliability of HPC
applications while maintaining application performance.

>>>>

Another option is to abandon the stricture of message passing within a procedural
programming language altogether.  The Open Community Runtime (OCR)
project\cite{OCR:wiki:url} provides an asynchronous task-based runtime designed for
machines with high-core count\cite{Dokulil20151453}, such as can be expected in any
exascale hardware design.  The project's goal is to create a framework and reference
implementation to help developers explore programming methods to improve the power
efficiency, programmability, and reliability of HPC applications while maintaining
application performance.
